Efficient pedigree recording for fast population genetics simulation

### 2018-01-12 forwards_paper.tex
numpy ref #57

The Tables API is primarily designed to facilitate efficient interchange of
data between programs or between different modules of the same program. We
adopted a `columnar' design, i.e., where all the values for a
particular column are stored in adjacent memory locations.
There are many advantages to columnar storage---for example, since adjacent
values in memory are from the same column, they tend to compress well,
and suitable encodings can be chosen on a per-column basis~\citep{abadi2006integrating}.
A particular advantage of this approach is that it enables very
efficient copying of data, and in principle zero-copy data access
(where a data consumer reads directly from the memory of a producer) is possible.
Our implementation uses the NumPy C API~\citep{walt2011numpy} to efficiently copy
data from Python into the low-level C library used to manipulate tree sequences.
This architecture allows for data transfer rates of gigabytes per second
(impossible under any text-based approach), while retaining excellent portability.
NumPy's array interface provides a great deal of flexibility and efficiency,
and makes it straightforward to transfer data from sources
such as HDF5 \citep{hdf5}or Dask~\citep{dask}.
For small scale data and debugging purposes, a simple text based format is also supported.

>>>>

The Tables API is primarily designed to facilitate efficient interchange of
data between programs or between different modules of the same program. We
adopted a `columnar' design, i.e., where all the values for a
particular column are stored in adjacent memory locations.
There are many advantages to columnar storage---for example, since adjacent
values in memory are from the same column, they tend to compress well,
and suitable encodings can be chosen on a per-column basis~\citep{abadi2006integrating}.
A particular advantage of this approach is that it enables very
efficient copying of data, and in principle zero-copy data access
(where a data consumer reads directly from the memory of a producer) is possible.
Our implementation 
% uses the NumPy C API~\citep{walt2011numpy} to efficiently copy
efficiently copies data from Python as a NumPy array \citep{walt2011numpy} 
into the low-level C library used to manipulate tree sequences.
This architecture allows for data transfer rates of gigabytes per second
(impossible under any text-based approach), while retaining excellent portability.
NumPy's array interface provides a great deal of flexibility and efficiency,
and makes it straightforward to transfer data from sources
such as HDF5 \citep{hdf5}or Dask~\citep{dask}.
For small scale data and debugging purposes, a simple text based format is also supported.
